\shapepar{\starshape}
A new game that is explained quickly yet that 
remains 
fascinating for years. 
Two players play in 20 min. Three or four players
may take up to 90. 
No dice involved. Suitable for all  from
age~5. A game by Jan \noun{Suchanek.} 
4$\times$5 coloured figures, 5 black and
5 grey blocks, the board.
\textsf{\textbf{Choose your figures: }}
Every player has five figures. There is one team of figures per player in the box. 
You have a blue, a red, a white, a green and a yellow figure. 
They start at the five corners of the board matching their colour.
They want to reach the big stops in the middle, where they move out.
\textsf{\textbf{Setup: } }
Put your figures on the big corners at the ring matching their body colours: 
your white figure on the white corner at the ring, your blue figure on the blue corner at the ring, etc.
Put the black blocks on the five crossings in the middle of the board. 
Park the grey blocks in the middle for later. 
\textsf{\textbf{Objective: }}
White figures want to go to the white crossing in the centre, blue
ones to the blue crossing, etc. The destination is always the big
coloured stop in the middle pentagon opposite the starting point.
Be the first to move \emph{three} pieces to their destinations to win.
\textsf{\textbf{The Rules: }}
Move any of your figures on the star or the ring in any direction as far as you please. 
You can turn at any free corner or crossing without stopping.
Never jump\textemdash neither over blocks, nor over any figures. 
But you may move \emph{onto} an occupied stop:
If you thereby beat a black block, place it on a free stop of your choice.
If you thereby move onto a stop with another figure, swap position with it.
You may swap the positions of two of your own figures. 
If you move onto a stop with multiple figures, choose one to swap with.
Do not make the very same move twice in immediate succession.  
A figure that has reached its destination is removed. Put it into the centre of the board. Then take one of the grey blocks and put it on a free stop of your choice.
If you beat such a grey block, take it from the board again.
If another player has  moved you to your goal, you \emph{must }move out once it is your turn.  
The last round gets played out.
$\!\!\star$   $\star$%